Fission product decay chain equilibria in \zirconia

### 2019-01-25 manuscript.tex
Fix legends

Nuclear fuel claddings have unique materials challenges associated with them owing to the highly active environment and creation of unstable isotopes. Corrosive species in the pin such as iodine can be produced directly as a result of fission of uranium fuel. While it is known that iodine plays a role in SCC, one must also consider that these iodine nuclei are unstable. Fission of uranium will produce iodine precursors, mainly unstable isotopes of tellurium. Both iodine and tellurium are relatively common fission products, with combined independent yields from thermal fission of U$_{235}$ above 5\% \cite{kennett1956mass, iodine129fissionyield, imanishi1976independent, iaeafissionyields, iodine132, amiel1975odd}. \\

@@

Defect volumes were calculated by completely relaxing an unconstrained, defective supercell using the geometry optimisation task. This allows the defective supercell to alter its volume in order to minimise the total energy of the system, at which point this 'optimal' supercell volume is recorded. The non-defective supercell volume, calculated in the same way, is then subtracted from the defective supercell volume to give the individual defect volume.

@@

%\lhead{\emph{References}} % Change the page header to say "References"
\bibliographystyle{unsrt}
\bibliography{Mendeley} % The references (bibliography) information are stored in the file named "Bibliography.bib"

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, ylabel={\ch{log_{10}}([D]) (per f.u.)}, ymin=-20, ymax=0, xmin=-35, xmax=0, legend style={{draw=}, at={(0.30,1.47)}, anchor=north west, legend columns=3, nodes={scale=0.75, transform shape}}]
        \addplot[no marks, draw=blue!70!black] table [x=pO2, y=electrons,]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{e^{'}}}; %\node at (-26.0,-1.9) {\ch{e^{'}}};
        \addplot[no marks, draw=red!85!black] table [x=pO2, y=holes,]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{h^{\textperiodcentered}}}; %\node at (-7,-3.6) {\ch{h^{\textperiodcentered}}};
        \addplot[no marks, draw=black!70!green] table [x=pO2, y=VO{2},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{V_{O}^{\textperiodcentered\textperiodcentered}}}; %\node at (-26.7,-3.3) {\ch{V_{O}^{\textperiodcentered\textperiodcentered}}};
         \addplot[no marks, draw=black!55!green] table [x=pO2, y=VO{1},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{V_{O}^{\textperiodcentered}}};
         \addplot[no marks, draw=black!30!green] table [x=pO2, y=VO{0},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{V_{O}^{x}}};

@@

         \addplot[no marks, draw=yellow!65!blue] table [x=pO2, y=VM{-2},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{''}}};
         \addplot[no marks, draw=yellow!55!blue] table [x=pO2, y=VM{-1},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{'}}};
         \addplot[no marks, draw=yellow!45!blue] table [x=pO2, y=VM{0},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{x}}};

@@

         \addplot[no marks, draw=green!80!pink] table [x=pO2, y=Mi{4},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered\textperiodcentered\textperiodcentered\textperiodcentered}}};
         \addplot[no marks, draw=green!70!pink] table [x=pO2, y=Mi{3},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered\textperiodcentered\textperiodcentered}}};
         \addplot[no marks, draw=green!60!pink] table [x=pO2, y=Mi{2},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textbf{\textperiodcentered\textperiodcentered}}}};
        \addplot[no marks, draw=green!50!pink] table [x=pO2, y=Mi{1},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered}}};
         \addplot[no marks, draw=green!40!pink] table [x=pO2, y=Mi{0},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{x}}};

@@

%\node at (-33.7,-0.5) {\textbf{a)}};

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, yticklabels={}, ymin=-20, ymax=0, xmin=-35, xmax=0]
        \addplot[no marks, draw=blue!70!black] table [x=pO2, y=electrons,]{dat/te_tet_10-3.dat}; %\node at (-27,-1.7) {\ch{e^{'}}};

@@

         \addplot[no marks, draw=black!55!green] table [x=pO2, y=VO{1},]{dat/te_tet_10-3.dat}; 
         \addplot[no marks, draw=black!30!green] table [x=pO2, y=VO{0},]{dat/te_tet_10-3.dat}; 

@@

        \addplot[no marks, dashed, draw=blue!50!white] table [x=pO2, y=TesubO{1},]{dat/te_tet_10-3.dat}; %\node at (-11,-2.6) {\ch{I_{O}^{\textperiodcentered}}};
        \addplot[no marks, dashed, draw=green!60!black] table [x=pO2, y=TesubO{2},]{dat/te_tet_10-3.dat}; 

@@

%\node at (-33.7,-0.5) {\textbf{b)}};

@@

\begin{figure}[htp] % Tet conc sweep

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, ylabel={\ch{log_{10}}([D]) (per f.u.)}, ymin=-20, ymax=0, xmin=-35, xmax=0, legend style={{draw=}, at={(0.40,0.97)}, anchor=north west, legend columns=3, nodes={scale=0.75, transform shape}}]

@@

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, yticklabels={}, ymin=-20, ymax=0, xmin=-35, xmax=0]

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, ylabel={\ch{log_{10}}([D]) (per f.u.)}, ymin=-20, ymax=0, xmin=-35, xmax=0, legend style={{draw=}, at={(0.30,1.47)}, anchor=north west, legend columns=3, nodes={scale=0.75, transform shape}}]
        \addplot[no marks, draw=blue!70!black] table [x=pO2, y=electrons,]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{e^{'}}}; %\node at (-26.0,-1.9) {\ch{e^{'}}};
        \addplot[no marks, draw=red!85!black] table [x=pO2, y=holes,]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{h^{\textperiodcentered}}}; %\node at (-7,-3.6) {\ch{h^{\textperiodcentered}}};

@@

         \addplot[no marks, draw=black!55!green] table [x=pO2, y=VO{1},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{V_{O}^{\textperiodcentered}}};
         \addplot[no marks, draw=black!30!green] table [x=pO2, y=VO{0},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{V_{O}^{x}}};

@@

         \addplot[no marks, draw=yellow!65!blue] table [x=pO2, y=VM{-2},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{''}}};
         \addplot[no marks, draw=yellow!55!blue] table [x=pO2, y=VM{-1},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{'}}};
         \addplot[no marks, draw=yellow!45!blue] table [x=pO2, y=VM{0},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{x}}};

@@

         \addplot[no marks, draw=red!50!yellow] table [x=pO2, y=Oi{-1},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{O_{i}^{'}}};
         \addplot[no marks, draw=red!40!yellow] table [x=pO2, y=Oi{0},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{O_{i}^{x}}};
         \addplot[no marks, draw=green!80!pink] table [x=pO2, y=Mi{4},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered\textperiodcentered\textperiodcentered\textperiodcentered}}};
         \addplot[no marks, draw=green!70!pink] table [x=pO2, y=Mi{3},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered\textperiodcentered\textperiodcentered}}};
         \addplot[no marks, draw=green!60!pink] table [x=pO2, y=Mi{2},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textbf{\textperiodcentered\textperiodcentered}}}};
        \addplot[no marks, draw=green!50!pink] table [x=pO2, y=Mi{1},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered}}};
         \addplot[no marks, draw=green!40!pink] table [x=pO2, y=Mi{0},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{x}}};

@@

         \addplot[no marks, draw=black!55!green] table [x=pO2, y=VO{1},]{dat/xe_tet_10-3.dat}; 
         \addplot[no marks, draw=black!30!green] table [x=pO2, y=VO{0},]{dat/xe_tet_10-3.dat}; 

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, ylabel={\ch{log_{10}}([D]) (per f.u.)}, ymin=-20, ymax=0, xmin=-35, xmax=0, legend style={{draw=}, at={(0.30,1.47)}, anchor=north west, legend columns=3, nodes={scale=0.75, transform shape}}]
        \addplot[no marks, draw=blue!70!black] table [x=pO2, y=electrons,]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{e^{'}}}; %\node at (-26.0,-1.9) {\ch{e^{'}}};
        \addplot[no marks, draw=red!85!black] table [x=pO2, y=holes,]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{h^{\textperiodcentered}}}; %\node at (-7,-3.6) {\ch{h^{\textperiodcentered}}};
        \addplot[no marks, draw=black!70!green] table [x=pO2, y=VO{2},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{V_{O}^{\textperiodcentered\textperiodcentered}}}; %\node at (-26.7,-3.3) {\ch{V_{O}^{\textperiodcentered\textperiodcentered}}};
         \addplot[no marks, draw=black!55!green] table [x=pO2, y=VO{1},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{V_{O}^{\textperiodcentered}}};
         \addplot[no marks, draw=black!30!green] table [x=pO2, y=VO{0},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{V_{O}^{x}}};

@@

         \addplot[no marks, draw=yellow!75!blue] table [x=pO2, y=VM{-3},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{'''}}};
         \addplot[no marks, draw=yellow!65!blue] table [x=pO2, y=VM{-2},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{''}}};
         \addplot[no marks, draw=yellow!55!blue] table [x=pO2, y=VM{-1},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{'}}};
         \addplot[no marks, draw=yellow!45!blue] table [x=pO2, y=VM{0},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{x}}};

@@

         \addplot[no marks, draw=red!50!yellow] table [x=pO2, y=Oi{-1},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{O_{i}^{'}}};
         \addplot[no marks, draw=red!40!yellow] table [x=pO2, y=Oi{0},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{O_{i}^{x}}};
         \addplot[no marks, draw=green!80!pink] table [x=pO2, y=Mi{4},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered\textperiodcentered\textperiodcentered\textperiodcentered}}};
         \addplot[no marks, draw=green!70!pink] table [x=pO2, y=Mi{3},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered\textperiodcentered\textperiodcentered}}};
         \addplot[no marks, draw=green!60!pink] table [x=pO2, y=Mi{2},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textbf{\textperiodcentered\textperiodcentered}}}};
        \addplot[no marks, draw=green!50!pink] table [x=pO2, y=Mi{1},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered}}};
         \addplot[no marks, draw=green!40!pink] table [x=pO2, y=Mi{0},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{x}}};

@@

         \addplot[no marks, draw=black!55!green] table [x=pO2, y=VO{1},]{dat/cs_tet_10-3.dat}; 
         \addplot[no marks, draw=black!30!green] table [x=pO2, y=VO{0},]{dat/cs_tet_10-3.dat}; 

>>>>

Nuclear fuel claddings have unique materials challenges associated with them owing to the highly active environment and creation of unstable isotopes. Corrosive species in the pin such as iodine can be produced directly as a result of fission of uranium fuel. While it is known that iodine plays a role in SCC, one must also consider that these iodine nuclei are unstable. Fission of uranium will produce iodine precursors, mainly unstable isotopes of tellurium. Both iodine and tellurium are relatively common fission products, with combined independent yields from thermal fission of U$_{235}$ above 5\% \cite{kennett1956mass, iodine129fissionyield, imanishi1976independent, iaeafissionyield, iodine132, amiel1975odd}. \\

@@

Defect volumes were calculated by completely relaxing an unconstrained, defective supercell using the geometry optimisation task in CASTEP. This allows the defective supercell to alter its volume in order to minimise the total energy of the system, at which point this `optimal' supercell volume is recorded. The non-defective supercell volume, calculated in the same way, is then subtracted from the defective supercell volume to give the individual defect volume.

@@

%\lhead{\emph{References}} % Change the page header to say "References"
\bibliographystyle{unsrt}
\bibliography{Mendeley, Bibliography} % The references (bibliography) information are stored in the file named "Bibliography.bib"

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, ylabel={\ch{log_{10}}([D]) (per f.u.)}, ymin=-10, ymax=0, xmin=-35, xmax=0, legend style={{draw=}, at={(0.30,1.47)}, anchor=north west, legend columns=3, nodes={scale=0.75, transform shape}}]
        \addplot[no marks, draw=blue!70!black] table [x=pO2, y=electrons,]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{e^{'}}}; \node at (-26.0,-1.9) {\ch{e^{'}}};
        \addplot[no marks, draw=red!85!black] table [x=pO2, y=holes,]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{h^{\textperiodcentered}}}; \node at (-7,-3.6) {\ch{h^{\textperiodcentered}}};
        \addplot[no marks, draw=black!70!green] table [x=pO2, y=VO{2},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{V_{O}^{\textperiodcentered\textperiodcentered}}}; \node at (-26.7,-3.3) {\ch{V_{O}^{\textperiodcentered\textperiodcentered}}};
         %\addplot[no marks, draw=black!55!green] table [x=pO2, y=VO{1},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{V_{O}^{\textperiodcentered}}};
         %\addplot[no marks, draw=black!30!green] table [x=pO2, y=VO{0},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{V_{O}^{x}}};

@@

         %\addplot[no marks, draw=yellow!65!blue] table [x=pO2, y=VM{-2},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{''}}};
         %\addplot[no marks, draw=yellow!55!blue] table [x=pO2, y=VM{-1},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{'}}};
         %\addplot[no marks, draw=yellow!45!blue] table [x=pO2, y=VM{0},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{x}}};

@@

         %\addplot[no marks, draw=green!80!pink] table [x=pO2, y=Mi{4},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered\textperiodcentered\textperiodcentered\textperiodcentered}}};
         %\addplot[no marks, draw=green!70!pink] table [x=pO2, y=Mi{3},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered\textperiodcentered\textperiodcentered}}};
         %\addplot[no marks, draw=green!60!pink] table [x=pO2, y=Mi{2},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textbf{\textperiodcentered\textperiodcentered}}}};
        %\addplot[no marks, draw=green!50!pink] table [x=pO2, y=Mi{1},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered}}};
         %\addplot[no marks, draw=green!40!pink] table [x=pO2, y=Mi{0},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{x}}};

@@

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, yticklabels={}, ymin=-10, ymax=0, xmin=-35, xmax=0]
        \addplot[no marks, draw=blue!70!black] table [x=pO2, y=electrons,]{dat/te_tet_10-3.dat}; \node at (-27,-1.7) {\ch{e^{'}}};

@@

         %\addplot[no marks, draw=black!55!green] table [x=pO2, y=VO{1},]{dat/te_tet_10-3.dat}; 
         %\addplot[no marks, draw=black!30!green] table [x=pO2, y=VO{0},]{dat/te_tet_10-3.dat}; 

@@

        \addplot[no marks, dashed, draw=blue!50!white] table [x=pO2, y=TesubO{1},]{dat/te_tet_10-3.dat}; 
        \addplot[no marks, dashed, draw=green!60!black] table [x=pO2, y=TesubO{2},]{dat/te_tet_10-3.dat}; \node at (-11,-2.6) {\ch{Te_{O}^{\textperiodcentered\textperiodcentered}}};

@@

@@

\begin{figure}[htp] % Iodine

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, ylabel={\ch{log_{10}}([D]) (per f.u.)}, ymin=-10, ymax=0, xmin=-35, xmax=0, legend style={{draw=}, at={(0.40,0.97)}, anchor=north west, legend columns=3, nodes={scale=0.75, transform shape}}]

@@

\begin{tikzpicture} % Iodine 2

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, yticklabels={}, ymin=-10, ymax=0, xmin=-35, xmax=0]

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, ylabel={\ch{log_{10}}([D]) (per f.u.)}, ymin=-10, ymax=0, xmin=-35, xmax=0, legend style={{draw=}, at={(0.30,1.47)}, anchor=north west, legend columns=3, nodes={scale=0.75, transform shape}}]
        \addplot[no marks, draw=blue!70!black] table [x=pO2, y=electrons,]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{e^{'}}}; \node at (-26.0,-1.9) {\ch{e^{'}}};
        \addplot[no marks, draw=red!85!black] table [x=pO2, y=holes,]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{h^{\textperiodcentered}}}; \node at (-7,-3.6) {\ch{h^{\textperiodcentered}}};

@@

         %\addplot[no marks, draw=black!55!green] table [x=pO2, y=VO{1},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{V_{O}^{\textperiodcentered}}};
         %\addplot[no marks, draw=black!30!green] table [x=pO2, y=VO{0},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{V_{O}^{x}}};

@@

         %\addplot[no marks, draw=yellow!65!blue] table [x=pO2, y=VM{-2},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{''}}};
         %\addplot[no marks, draw=yellow!55!blue] table [x=pO2, y=VM{-1},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{'}}};
         %\addplot[no marks, draw=yellow!45!blue] table [x=pO2, y=VM{0},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{x}}};

@@

         %\addplot[no marks, draw=red!50!yellow] table [x=pO2, y=Oi{-1},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{O_{i}^{'}}};
         %\addplot[no marks, draw=red!40!yellow] table [x=pO2, y=Oi{0},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{O_{i}^{x}}};
         %\addplot[no marks, draw=green!80!pink] table [x=pO2, y=Mi{4},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered\textperiodcentered\textperiodcentered\textperiodcentered}}};
         %\addplot[no marks, draw=green!70!pink] table [x=pO2, y=Mi{3},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered\textperiodcentered\textperiodcentered}}};
         %\addplot[no marks, draw=green!60!pink] table [x=pO2, y=Mi{2},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textbf{\textperiodcentered\textperiodcentered}}}};
        %\addplot[no marks, draw=green!50!pink] table [x=pO2, y=Mi{1},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered}}};
         %\addplot[no marks, draw=green!40!pink] table [x=pO2, y=Mi{0},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{x}}};

@@

         %\addplot[no marks, draw=black!55!green] table [x=pO2, y=VO{1},]{dat/xe_tet_10-3.dat}; 
         %\addplot[no marks, draw=black!30!green] table [x=pO2, y=VO{0},]{dat/xe_tet_10-3.dat}; 

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, ylabel={\ch{log_{10}}([D]) (per f.u.)}, ymin=-10, ymax=0, xmin=-35, xmax=0, legend style={{draw=}, at={(0.30,1.47)}, anchor=north west, legend columns=3, nodes={scale=0.75, transform shape}}]
        \addplot[no marks, draw=blue!70!black] table [x=pO2, y=electrons,]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{e^{'}}}; \node at (-26.0,-1.9) {\ch{e^{'}}};
        \addplot[no marks, draw=red!85!black] table [x=pO2, y=holes,]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{h^{\textperiodcentered}}}; \node at (-7,-3.6) {\ch{h^{\textperiodcentered}}};
        \addplot[no marks, draw=black!70!green] table [x=pO2, y=VO{2},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{V_{O}^{\textperiodcentered\textperiodcentered}}}; \node at (-26.7,-3.3) {\ch{V_{O}^{\textperiodcentered\textperiodcentered}}};
         %\addplot[no marks, draw=black!55!green] table [x=pO2, y=VO{1},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{V_{O}^{\textperiodcentered}}};
         %\addplot[no marks, draw=black!30!green] table [x=pO2, y=VO{0},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{V_{O}^{x}}};

@@

         %\addplot[no marks, draw=yellow!75!blue] table [x=pO2, y=VM{-3},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{'''}}};
         %\addplot[no marks, draw=yellow!65!blue] table [x=pO2, y=VM{-2},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{''}}};
         %\addplot[no marks, draw=yellow!55!blue] table [x=pO2, y=VM{-1},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{'}}};
         %\addplot[no marks, draw=yellow!45!blue] table [x=pO2, y=VM{0},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{x}}};

@@

         %\addplot[no marks, draw=red!50!yellow] table [x=pO2, y=Oi{-1},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{O_{i}^{'}}};
         %\addplot[no marks, draw=red!40!yellow] table [x=pO2, y=Oi{0},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{O_{i}^{x}}};
         %\addplot[no marks, draw=green!80!pink] table [x=pO2, y=Mi{4},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered\textperiodcentered\textperiodcentered\textperiodcentered}}};
         %\addplot[no marks, draw=green!70!pink] table [x=pO2, y=Mi{3},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered\textperiodcentered\textperiodcentered}}};
         %\addplot[no marks, draw=green!60!pink] table [x=pO2, y=Mi{2},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textbf{\textperiodcentered\textperiodcentered}}}};
        %\addplot[no marks, draw=green!50!pink] table [x=pO2, y=Mi{1},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{\textperiodcentered}}};
         %\addplot[no marks, draw=green!40!pink] table [x=pO2, y=Mi{0},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Zr_{i}^{x}}};

@@

         %\addplot[no marks, draw=black!55!green] table [x=pO2, y=VO{1},]{dat/cs_tet_10-3.dat}; 
         %\addplot[no marks, draw=black!30!green] table [x=pO2, y=VO{0},]{dat/cs_tet_10-3.dat}; 
